Cannibalism among the supermassive black holes

### 2018-04-26 paper.tex
Worked on merger tree data section.  Added bibliographic references.

\subsection{Merger tree}
Our merger tree data came from the SMBH evolution simulations of \citet{2015ApJ...799..178K}, which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.  The following cosmological parameters were used in their simulation:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.  The SMBHs were evolved from $4\geq z \geq 0$.

The merger tree data was in two primary files.  One file was centered around SMBHs at each redshift slice, giving information for the black hole's seed mass, accreted and seed mass, its host galaxy, the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).  The other file was centered on galaxies at each redshift slice, providing information on the galaxies' stellar mass, dark matter mass, central BH, and any orbiting black holes within the galaxy.

@@

@@

The authors would like to thank Andrea Kulier for providing merger tree data. AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.

>>>>

\subsection{Merger tree}
Our merger tree data came from two sources:
\begin{itemize}
\item Galactic merger tree data from simulations of \citet{2012MNRAS.425..641L} (hereafter Lackner12), which was centered on galaxies at each redshift slice, providing information on the galaxies' stellar mass, dark matter mass, central BH, and any orbiting black holes within the galaxy.
\item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15), which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.  The data was centered around SMBHs at each redshift slice between $z=4$ to $z=0$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
\end{itemize}

The following cosmological parameters were used in the simulations of both Lackner12 and Kulier15:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.

Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.  Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.  In order to adjust our stellar masses to levels more in line with current observations, we used observational data from \citet{2018AstL...44....8K}, in particular Figure 11. (SHOULD I ADD PLOT OF OUR ORIGINAL STELLAR DATA?  THE PLOT FROM KRAVTSOV WAS RECREATED BY EYEBALL WITH A FEW STRAIGHT LINES TO APPROXIMATE HIS CURVE.  HOW TO INCORPORATE THAT?)

@@

As in the simulations from Kulier12, the SMBHs were evolved from $z=4$ to $z=0$.

@@

The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data. AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.
